---
title: "Introduction to WorldbankAnalysis Package"
author: "Your Name"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to WorldbankAnalysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

This vignette demonstrates how to use the `WorldbankAnalysis` to analyze World Bank data, handle missing values, and build predictive models.

## Setup

Load the package and required libraries.

```{r setup, message=FALSE, warning=FALSE}
library(WorldbankAnalysis)
library(dplyr)
library(ggplot2)
library(tidyr)
library(readr)
library(readr)
library(Metrics)
library(ggplot2)
library(parallel)
library(zoo)
```

## Step 1: Fetch and Merge Data

Use the `fetch_merge_indicators` function to fetch and merge World Bank data. Here, we specify a list of World Bank indicator URLs.

```{r fetch-merge-data}
# Define the URLs for World Bank indicators
indicator_urls <- list(
  "life_expectancy" = "https://api.worldbank.org/v2/country/all/indicator/SP.DYN.LE00.IN?format=json",
  "inflation" = "https://api.worldbank.org/v2/country/all/indicator/FP.CPI.TOTL.ZG?format=json",
  "gdp_per_capita" = "https://api.worldbank.org/v2/country/all/indicator/NY.GDP.PCAP.CD?format=json",
  "undernourishment" = "https://api.worldbank.org/v2/country/all/indicator/SN.ITK.DEFC.ZS?format=json",
  "health_expenditure" = "https://api.worldbank.org/v2/country/all/indicator/SH.XPD.CHEX.PC.CD?format=json",
  "infant_mortality" = "https://api.worldbank.org/v2/country/all/indicator/SP.DYN.IMRT.IN?format=json"
)

# Fetch and merge data
merged_data <- fetch_merge_indicators(indicator_urls = indicator_urls, num_cores = 4, start_year = 2015, end_year = 2022)

# Display a preview of the merged data
head(merged_data)
```

## Step 2: Handle Missing Values

The `impute_data` function handles missing values in the dataset using the following approaches:
- **Linear Interpolation:** Missing values within a time series are imputed using linear interpolation (`zoo::na.approx`).
- **Global Mean Imputation:** Remaining missing values, which cannot be imputed by interpolation, are replaced with the global mean for the corresponding variable.

```{r handle-missing-values}
# Impute missing values
imputed_data <- impute_data(merged_data)

# Display a preview of the imputed data
head(imputed_data)
```

## Step 3: Run the Analysis

Run the complete analysis workflow using the `run_analysis` function. This step includes:
- Data preparation
- PCA for dimensionality reduction
- Training multiple models
- Evaluating models
- Plotting predictions vs. actual values

```{r run-analysis}
# Run the analysis
results <- run_analysis(
  imputed_data = imputed_data,
  target_year = 2021,
  filter_vars = c("inflation", "gdp_per_capita", "health_expenditure", "infant_mortality", "undernourishment"),
  model_list = c("lm", "rf", "svm", "gbm"),
  split_ratio = 0.7,  # Use 70% of the data for training
  pca_variance_threshold = 0.9  # Retain 90% of variance in PCA
)

# Extract evaluation results and plot
evaluation_results <- results$evaluation
evaluation_plot <- results$plot
```

### Model Evaluation

```{r model-evaluation}
# Display evaluation metrics
evaluation_results
```

### Predictions vs. Actual Plot

```{r prediction-plot, fig.width=8, fig.height=6}
# Display the plot
print(evaluation_plot)
```

## Conclusion

This vignette demonstrated the complete workflow for using `WorldbankAnalysis`. From fetching and preprocessing data to building and evaluating predictive models, the package simplifies the analytical workflow.

```
